Decentralised location proof system

### 2016-04-23 thesis/background.tex
Adding final updates

\section{Proving location}
As an increasing amount of personal information is accessible on the internet and therefore on mobile devices, the security that previously existed by requiring physical interaction between humans to transfer sensitive data is lost.

Location proof is a large part of that security. There is currently no ubiquitous method of \textit{proving} a mobile user's location at a given time over the internet. Many companies, such as Netflix, use GeoIP databases such as MaxMind \cite{maxmind} to estimate a user's location based on its IP address. This is a location observation technique rather than a proof. It is therefore inaccurate and easily bypassable using proxy servers or VPNs.

@@

Better solutions to this problem exist. \textit{Location proof systems} allow users of the system to \textit{prove} their location to another user, by creating \textit{location proofs}. The structure of a location proof varies from system to system. In essence, a location proof is a piece of data, potentially signed or encrypted by another party, which attests the location of a user at a specific time. Examples of location proof systems are discussed in detail in section \ref{ssec:proof_systems}.

\section{Distributed and decentralised systems}
A \textit{distributed} system is a system which distributes the computation of a task across multiple nodes (computers) connected over a network. These nodes are assigned a task from a central node, and then work together and communicate to complete the task by passing messages to each other over the network \cite{distributed}.

For example, Google search indexes are not computed on just one node, rather on a network of nodes that communicate by sending messages to each other. Google therefore \textit{distributes} the task of calculating search indexes across multiple nodes. This has two main advantages; It is less time consuming, because different index calculations can be computed on different nodes at the same time, and it is scalable, because nodes can be added or removed from the network dynamically, to meet demand.

A \textit{decentralised} system is similar to a distributed system, except no node is in charge. Nodes in a decentralised network still communicate by passing messages to each other over the network, but unlike a distributed system, they are not assigned tasks by a central or master node. Bitcoin \cite{bitcoin} is a good example of a large-scale decentralised system. Two nodes in the Bitcoin network can choose to send money between themselves, creating a transaction. They make the details of that transaction public. The two nodes therefore create and publish the transaction without coordination from a central node.

In the context of this project, a distributed location proof system is considered to be a proof system where the task of facilitating user proof request and creation is distributed across multiple \textit{worker nodes}, which are controlled and coordinated by a central node. This allows a higher volume of proofs to be created concurrently compared with using a single node, while maintaining centralised and simple control over the system. This is shown in figure \ref{fig:distributed_location}.

@@

A decentralised location proof system is considered to be one where no node is in charge of controlling or coordinating the system. Nodes can create and publish location proofs between themselves, without the need for a central third party to coordinate their interaction (figure \ref{fig:decentralised_location}). This makes coordination more complex, but means that no node is considered to be ``in charge'' of the system.

@@

A hardware technique \cite{brassil}, developed by Brassil et al. of HP Laboratories, operates by supplementing existing Wi-Fi access points (\textit{AP's}) with \textit{femtocells}. A femtocell \cite{femtocell} is a small cellular antenna that connects to a mobile network operator (such as Vodafone) via the Internet, which allows mobile networks (e.g. networks used for calls and texts) to be extended on demand. Location verification over the internet is made possible by determining which femtocell a mobile node is connected to as it transfers data over Wi-Fi. This is possible because the central server in the location verification system has access to the mobile operator's user data.

This solution requires investment in additional hardware to supplement existing Wi-Fi access points, and requires access to mobile providers' user databases to identify users' locations (see figure \ref{fig:hp_labs}). Note that the two lines between the user and the AP in figure \ref{fig:hp_labs} indicates that the user is connected to the AP \textit{and} its attached femtocell.

\begin{figure}[H]
\begin{center}
\resizebox {0.45\columnwidth} {!} {\includegraphics{diagrams/hp_paper.png}}
\caption{Hardware-based proof system (Adapted from Brassil et al. \cite{brassil})}
\label{fig:hp_labs}
\end{center}
\end{figure}

The use of a centralised system, as described in figure \ref{fig:hp_labs}, creates security, privacy and vulnerability issues. An attacker who succeeds in compromising the security of the central server can create unlimited false location proofs for itself, or violate the privacy of the users of the system, and potentially track their location. This is because in this system, location proof data resides with the central server. This means that the user has no control over the security of their proofs, and an attacker could seize them. The central system architecture is also vulnerable, in the sense that a resource availability attack such as a DDoS attack \cite{ddos} could render the central architecture unavailable, making location verification unavailable.
\\

Luo et al. propose a system that uses software installed on Wi-Fi access points to allow users to create location proofs \cite{luo}. In their system, each access point is given a \textit{group signature} by a central server, and can sign location proofs for users (figure \ref{fig:luo_diagram}).

\begin{figure}[H]
\begin{center}
\resizebox {0.5\columnwidth} {!} {\includegraphics{diagrams/ap_paper.png}}
\caption{Distributed proof system on access points (Adapted from Luo et al. \cite{luo})}
\label{fig:luo_diagram}
\end{center}
\end{figure}

@@

\begin{figure}[H]
\begin{center}
\resizebox {0.65\columnwidth} {!} {\input{diagrams/luo_transaction.tex}}
\caption{Proof request with group signature (Adapted from Luo et al. \cite{luo})}
\label{fig:luo_transaction}
\end{center}
\end{figure}

@@

This system creates \textit{proactive} location proofs. A proactive location proof is one which is created before it is needed. The user creates application-independent location proofs, and can use them at a later time with any application(s) it chooses.
\\

A system proposed by Khan et al. takes a different approach, by using other users as witnesses to a location claim \cite{khan}. In this system, a \textit{witness} physically located near the user is used by the central server to verify the user's location claim (figure \ref{fig:witness_paper}). Like the model proposed by Luo et al., this system allows the user to have control over their own privacy, as the user owns the location proof.

@@

\section{Blockchain}
In Bitcoin \cite{bitcoin}, the entire transaction history is stored in the \textit{blockchain}. This is a decentralised, append-only ledger (database) \cite{blueprint}. The blockchain is maintained by a network of \textit{miner} nodes competing to collect transactions into a new block, sign that block by solving a difficult puzzle known as a \textit{proof-of-work}, and append it to the ledger. It is used in Bitcoin to enforce consensus; every miner in the network agrees that all blocks in the blockchain are valid, due to the presence of their associated proof-of-work.

@@

\section{Design goals} \label{sec:design_goals}
Before designing the system, a number of goals must be defined and an attempt made to satisfy them in the design. The design goals of this project are listed below.

\begin{enumerate}
	\item The system must be \textit{privacy preserving}. It must not be possible for a malicious user to obtain any additional information from an honest user other than the information the honest user intended to release.
	\item False location proofs must be detectable. It must be possible to detect any location proofs attempting to prove false information.
	\item The system must be decentralised, and cannot rely on any central nodes. This is discussed in section \ref{ssec:centralised}.
	\item The design must conform to the desirable properties defined in OTIT (discussed in section \ref{ssec:otit}).
	\item The system must not be vulnerable to any known threats (section \ref{ssec:threats}).
\end{enumerate}

\subsection{Central services} \label{ssec:centralised}
Location proof systems which rely on central nodes, such as those discussed in section \ref{ssec:proof_systems}, have a fundamental weakness. These systems assume that the central node is honest, always available, and cannot be compromised by an attacker. Since the central node is in charge of coordinating the system, compromising it allows an attacker potentially unlimited control over the system. This completely violates a user's privacy, as the central node may contain sensitive information about users and their location, or a means of retrieving sensitive information, such as decryption keys. Users of the system also have to assume that the central node is available at all times, otherwise the system is considered unavailable, or ``down''.

These problems do not occur in a decentralised location proof system, because no node is considered to be ``in charge''. If no node is in charge, any node(s) can join or leave the network without altering the state of the network, or making any services unavailable. This lack of authority prevents privacy breaches, but presents other issues. System coordination, which is easily maintained by the central node in a centralised system, is now maintained by each participant in the decentralised system, who may or may not all be honest.

\subsection{OTIT} \label{ssec:otit}
Khan et al. present the \textit{OTIT} model, a ``model for designing secure location provenance'' \cite{otit}. It defines the following 8 desirable properties of a location proof system:
\begin{itemize}
	\item[] \textbf{Chronological}: Location proofs should be ordered according to the sequence of their creation.
	\item[] \textbf{Order preserving}: The order in which the proofs are entered into the proof chain should always be maintained.
	\item[] \textbf{Verifiable}: A Verifier should be able to verify or reject the claim by the user that it has visited the given location(s).
	\item[] \textbf{Tamper evident}: A Verifier should be able to detect if the proof chain has been tampered with or modified by an unauthorised party.
	\item[] \textbf{Privacy preserved}: When the proof chain is verified for specific location proofs, privacy is preserved for the other location proofs within the chain.
	\item[] \textbf{Selective In-sequence privacy}: The user should be able to choose not to reveal some location proofs within the proof chain when seeking verification.
	\item[] \textbf{Privacy protected chronology}: The system should ensure that the user does not hide important information from the items within the subset of the proof chain.
	\item[] \textbf{Convenience and derivability}: The system should ensure that the user does not burden the Verifier with a large amount of data to analyse in order to verify its location.
\end{itemize}

\subsection{Threats} \label{ssec:threats}
A number of related publications \cite{luo,khan} have identified various potential threats (or attacks) on location verification systems. These are outlined below.

@@

>>>>

\section{Proving location}
An increasing amount of personal information is accessible on the internet, and therefore on mobile devices. Hence the security that previously existed by requiring physical interaction between humans to transfer sensitive data is lost.

Location proof is a large part of that security. There is currently no ubiquitous method of \textit{proving} a mobile user's location at a given time over the internet. This problem will become increasingly pronounced as the amount of personal information accessible on the internet increases. For example, banks wishing to reduce fraud may soon benefit from requiring a user to prove its location before logging in to their mobile banking application. A feature like this is impossible without an underlying ubiquitous location proof system.

Many companies, such as Netflix, use GeoIP databases such as MaxMind \cite{maxmind} to estimate a user's location based on its IP address. This is a location observation technique rather than a proof. It is therefore inaccurate and easily bypassable using proxy servers or VPNs.

@@

However, more rigorous solutions to the problem of determining a user's location exist. \textit{Location proof systems} allow users of the system to \textit{prove} their location to another user, by creating \textit{location proofs}. The structure of a location proof varies from system to system. In essence, a location proof is a piece of data, potentially signed or encrypted by another party, which attests the location of a user at a specific time. Examples of location proof systems are discussed in detail in section \ref{ssec:proof_systems}.

\section{Distributed and decentralised systems}
A \textit{distributed} system is a system which distributes the computation of a task across multiple nodes connected over a network. These nodes are assigned a task from a central node, then proceed to work together and communicate to complete the task by passing messages to each other over the network \cite{distributed}.

For example, Google search indexes are not computed on just one node, but rather on a network of nodes that communicate by sending messages to each other. Google therefore \textit{distributes} the task of calculating search indexes across multiple nodes. This has two main advantages: It is less time consuming, because different index calculations can be computed on different nodes at the same time, and it is scalable, because nodes can be added or removed from the network dynamically, to meet demand.

A \textit{decentralised} system is similar to a distributed system, except there is no central node. Nodes in a decentralised network still communicate by passing messages to each other over the network but, unlike a distributed system, they are not assigned tasks by a central or master node. A well-known example of a large-scale decentralised system is Bitcoin \cite{bitcoin}. Two nodes in the Bitcoin network can choose to send money between themselves, creating a transaction. The transaction details are then made public. The two nodes therefore create and publish the transaction without coordination from a central node.

In the context of this project, a distributed location proof system is considered to be a proof system where the task of facilitating user proof request and creation is distributed across multiple \textit{worker nodes}. These are controlled and coordinated by a central node. This allows a higher volume of proofs to be created concurrently compared with using a single node, while maintaining centralised and simple control over the system. This is shown in figure \ref{fig:distributed_location}.

@@

A decentralised location proof system is considered to be one where no central node controls or coordinates the system. Nodes can create and publish location proofs between themselves, without the need for a central third party to coordinate their interaction (figure \ref{fig:decentralised_location}). This makes coordination more complex, but removes the threats associated with using a central node to store and issue location proofs.

@@

A hardware technique \cite{brassil}, developed by Brassil et al. of HP Laboratories, operates by supplementing existing Wi-Fi access points (\textit{AP's}) with \textit{femtocells}. A femtocell \cite{femtocell} is a small cellular antenna that connects to a mobile network operator (such as Vodafone) via the Internet, which allows mobile networks (e.g. networks used for calls and SMS messages) to be extended on demand. Location verification over the internet is made possible by determining which femtocell a mobile node is connected to as it transfers data over Wi-Fi. This is possible because the central server in the location verification system has access to the mobile operator's user data.

However, this solution requires investment in additional hardware to supplement existing Wi-Fi access points, and requires access to mobile providers' user databases to identify users' locations (see figure \ref{fig:hp_labs}).

\begin{figure}[H]
\begin{center}
\resizebox {0.45\columnwidth} {!} {\includegraphics{diagrams/hp_paper.png}}
\caption[Hardware-based proof system]{Hardware-based proof system (Adapted from Brassil et al. \cite{brassil}). Note that the two lines between the user and the AP indicates that the user is connected to the AP \textit{and} its attached femtocell.}
\label{fig:hp_labs}
\end{center}
\end{figure}

The use of a centralised system, as described in figure \ref{fig:hp_labs}, creates security, privacy and vulnerability issues. An attacker who succeeds in compromising the security of the central server can create unlimited false location proofs for itself, or it can violate the privacy of the users of the system, and potentially track their location. This is because in this system, location proof data resides with the central server. Thus the user has no control over the security of their proofs, and an attacker could seize them. The central system architecture is vulnerable to other problems, such as central node hardware failure, or resource availability attacks. For example, a DDoS attack \cite{ddos} could render the central architecture unavailable, making location verification unavailable.
\\

Another approach by Luo et al. proposes a system that uses software installed on Wi-Fi access points to allow users to create location proofs \cite{luo}. In their system, each access point is given a \textit{group signature} by a central server, and can sign location proofs for users (figure \ref{fig:luo_diagram}).

\begin{figure}[H]
\begin{center}
\resizebox {0.5\columnwidth} {!} {\includegraphics{diagrams/ap_paper.png}}
\caption[Distributed proof system on access points]{Distributed proof system on access points (Adapted from Luo et al. \cite{luo})}
\label{fig:luo_diagram}
\end{center}
\end{figure}

@@

\begin{figure}[H]
\begin{center}
\resizebox {0.65\columnwidth} {!} {\input{diagrams/luo_transaction.tex}}
\caption[Proof request with group signature]{Proof request with group signature (Adapted from Luo et al. \cite{luo})}
\label{fig:luo_transaction}
\end{center}
\end{figure}

@@

Unlike the system proposed by Brassil et al., this system creates \textit{proactive} location proofs. A proactive location proof is one which is created before it is needed. The user creates application-independent location proofs, and can use them at a later time with any application(s) it chooses. This is essential in a decentralised proof system, where proofs \textit{cannot} be application dependent by definition.

Using a group signature allows the system to be very easily distributed, while still coordinated by a central node. However, a malicious user who attacks the central server and discovers the group signature can create unlimited false proofs for itself.
\\

A system proposed by Khan et al. takes a different approach, by using other users as witnesses to a location claim \cite{khan}. In this system, a \textit{witness} who is physically located near the user is used by the central server to verify the user's location claim (figure \ref{fig:witness_paper}). Like the model proposed by Luo et al., this system allows the user to have control over their own privacy, as the user owns the location proof.

@@

\section{Blockchain}
In a decentralised location proof system, location proofs cannot reside solely with the owner, as it would be difficult to detect proof tampering. Instead, existing decentralised systems such as Bitcoin \cite{bitcoin} store data publicly, but encrypt it with a key known only to the owner. In Bitcoin, this is made possible using a \textit{blockchain}, which provides a public, tamper-proof database for the transaction data. A decentralised location proof system can use a blockchain to store location proofs publicly, encrypted with a key known only to the user who created the proofs.

The blockchain is a decentralised, append-only ledger (database) \cite{blueprint}. It is maintained by a network of \textit{miner} nodes competing to collect transactions into a new block, sign that block by solving a difficult puzzle known as a \textit{proof-of-work}, and append it to the ledger. It is used in Bitcoin to enforce consensus; every miner in the network agrees that all blocks in the blockchain are valid, due to the presence of their associated proof-of-work.

@@

\section{Design goals} \label{sec:design_goals}
Before designing the system, a number of goals must be defined and an attempt made to satisfy them in the system design. The goals for this project were determined by examining the design goals of previous work \cite{brassil, luo, khan} discussed in section \ref{ssec:proof_systems}, which is considered to be the state of the art. This system must satisfy the same goals as these centralised proof systems, along with an additional goal of decentralisation.

\begin{enumerate}
	\item The system must be decentralised, and cannot rely on any central nodes. This is discussed in section \ref{ssec:centralised}.
	\item The design must conform to the desirable properties defined in OTIT (discussed in section \ref{ssec:otit}).
	\item The system must not be vulnerable to any known threats. Threats are identified in previous publications \cite{luo,khan}, which outline potential attacks on location proof systems (section \ref{ssec:threats}).
\end{enumerate}

\subsection{Central services} \label{ssec:centralised}
Location proof systems which rely on central nodes, such as those discussed in section \ref{ssec:proof_systems}, have a fundamental weakness. These systems assume that the central node is honest, always available, and cannot be compromised by an attacker. Since the central node is in charge of coordinating the system, compromising it allows an attacker to potentially take complete control over the system. This destroys the privacy of each user, as the central node may contain sensitive information about users and their location, or a means of retrieving sensitive information, such as decryption keys. Users of the system also have to trust that the central node is always available which, in reality, may not be true.

These problems do not occur in a decentralised location proof system, because all nodes have an equal level of authority. Any node(s) can join or leave the network without altering the state of the network, or without making any services unavailable. This lack of authority prevents privacy breaches, but presents other issues. System coordination, which is easily maintained by the central node in a centralised system, is now maintained by each participant in the decentralised system, who may or may not all be honest.

\subsection{OTIT} \label{ssec:otit}
Khan et al. present the \textit{OTIT} model, a ``model for designing secure location provenance'' \cite{otit}. It defines the 8 properties that all location proof systems should satisfy. This project will also aim to satisfy each of these properties, which are defined below.
\begin{itemize}
	\item[] \textbf{Chronological}: Location proofs should be ordered according to the sequence of their creation.
	\item[] \textbf{Order preserving}: The order in which the proofs are entered into the proof chain should always be maintained.
	\item[] \textbf{Verifiable}: A Verifier should be able to verify or reject the claim by the user that it has visited the given location(s).
	\item[] \textbf{Tamper evident}: A Verifier should be able to detect if the proof chain has been tampered with or modified by an unauthorised party.
	\item[] \textbf{Privacy preserved}: When the proof chain is verified for specific location proofs, privacy is preserved for the other location proofs within the chain.
	\item[] \textbf{Selective in-sequence privacy}: The user should be able to choose not to reveal some location proofs within the proof chain when seeking verification.
	\item[] \textbf{Privacy protected chronology}: The system should ensure that the user does not hide important information from the items within the subset of the proof chain.
	\item[] \textbf{Convenience and derivability}: The system should ensure that the user does not burden the Verifier with a large amount of data to analyse in order to verify its location.
\end{itemize}

\subsection{Threats} \label{ssec:threats}
A number of related publications \cite{luo,khan} have identified various potential threats (or attacks) on location proof systems. A threat on a location proof system is a potential vulnerability. Threats allow a malicious user (an attacker) to gain an advantage over other users by exploiting weaknesses in the system. In a location proof system, a threat could potentially allow a malicious user to create false proofs for itself, or violate another user's privacy.

This project will first introduce the threats being considered by defining them, then it will describe the proposed model of a decentralised location proof system, and finally analyse the model with respect to each defined threat. The threats considered in this project are a combination of all threats considered by Luo et al. \cite{luo} and Khan et al. \cite{khan} in their centralised location proof system models. These are defined below.

@@

This project aims to design a decentralised location proof system which satisfies the aforementioned requirements as well as addressing and mitigating the threats posed by malicious users to such a system.

### 2016-04-23 thesis/conclusion.tex
Adding final updates

\section{Future work}
There are many worthwhile areas for future work, because to the best of the author's knowledge, this is the first attempted design of a fully decentralised location proof system.

\subsection{Verification techniques}
Section \ref{ssec:verification} outlined a number of simple verification techniques that a Verifier node could use to analyse the a proof chain. There is potential for further research on advanced techniques of analysing proof chain trees to determine the validity of a user's proof request.

@@

\section{Conclusion}
This project presented the design of a decentralised location proof system. The aim of the project was to design a system that satisfied the design goals, as defined in section \ref{sec:design_goals}. This system satisfies all of the requirements of OTIT \cite{otit}, and all but one of the threats defined in section \ref{ssec:threats}. However, chapter \ref{ch:evaluation} concluded that this Sybil attack threat must be highly targeted to be effective.

In conclusion, the model presented in this project is a viable design of a decentralised location proof system, providing that the Sybil attack vulnerability can be heavily mitigated against or prevented outright.

>>>>

\section{Future work}
There are many worthwhile areas for future work, because to the best of the author's knowledge, this is the first attempted design of a fully decentralised location proof system. These are mentioned briefly below.

\subsection{Verification techniques}
Section \ref{ssec:verification} outlined a number of simple verification techniques that a Verifier node could use to analyse a proof chain. There is potential for further research on advanced techniques of analysing proof chain trees to determine the validity of a user's proof request.

@@

\section{Conclusion}
The aim of the project was to design a system that satisfied the design goals, as defined in section \ref{sec:design_goals}. This system satisfies all eight of the desirable properties of a location proof system as defined by OTIT \cite{otit}, and all but one of the threats defined in section \ref{ssec:threats}. However, chapter \ref{ch:evaluation} concluded that this Sybil attack threat must be highly targeted to be effective. Most Sybil attacks can be mitigated against using various techniques, and many simple Sybil attacks will be clearly visible to Verifiers without any mitigation whatsoever.

It is interesting to compare this system to existing centralised location proof systems by Khan et al. \cite{khan} and Luo et al. \cite{luo}. As discussed throughout this project, a decentralised solution to location proof generation is more resilient to attack than these centralised systems by design. However, when compared to both of these systems, the model presented in this project is more resilient against attacks such as wormhole attacks, weak identities and false assertion attacks. This resilience is not due purely to the decentralised nature of the model, but also to interesting properties of the design, such as identity generation.

This project has explained the shortcomings of centralised location proof systems, and it has presented a viable design of a decentralised location proof system, which is to the author's knowledge the first system design of its kind. This decentralised location proof system retains all of the desirable properties of current centralised location proof systems, and is more resilient to attack, as demonstrated during evaluation.

It can therefore be concluded that the advantages of this decentralised location proof system, along with its resilience to attack, make it an excellent candidate for a secure, ubiquitous location proof system.

### 2016-04-23 thesis/design.tex
Adding final updates

@@

\section{Identities}
In order to preserve users' privacy, a user will only ever use an identity for one transaction, before generating a new one. This prevents curious users from watching the public blockchain for a known identity and tracking it. However, to prevent identity theft, it is important for a Verifier to be able to prove that a mobile node is the owner of each identity. This is achieved using a public/private key pair for each mobile node.

@@

\subsection{Identity duplication}
Since all identities are generated from random nonces, there is nothing to prevent two nodes from generating the same identity and using it in different transactions. It is therefore possible that during verification, a Verifier node may find multiple transactions with the same ID while searching the blockchain. Verifiers are provided with decryption key from the requesting node for the transactions they are searching for, which will only successfully decrypt one of the transactions with the duplicate ID. A Verifier will try to decrypt each one until it finds the one that can be decrypted successfully.

\newpage
\section{Transactions} \label{sec:transactions}
During an exchange between two nodes, a number of different items must be shared and calculated. Figure \ref{fig:transaction} describes and explains an honest, successful exchange, assuming an ad-hoc network has already been set up between nodes $A$ and $B$.

@@

To abort the exchange, node $A$ terminates the ad-hoc network with node $M$, and won't publish anything onto the blockchain. This means that even if node $M$ fabricates some data from node $A$ and publishes a transaction onto the blockchain, the matching transaction from node $A$ will not be present, so node $M$'s transaction will be disregarded by any Verifiers.

\begin{figure}
\resizebox {\columnwidth} {!} {\input{diagrams/aborted_transaction.tex}}
\caption{An aborted transaction due to malicious node $M$}
\label{fig:aborted_transaction}
\end{figure}

@@

\begin{figure}[H]
\begin{center}
\resizebox {0.8\columnwidth} {!} {\input{diagrams/verify_request.tex}}
\caption{Verification request}
\label{fig:verify_request}
\end{center}
\end{figure}

\begin{itemize}[noitemsep,topsep=0pt]
	\item[] $\mathbf{ID_{A}[n-1]}$ is the ID of node $A$'s most recently published transaction. Note that $ID_A[n]$ has already been generated, but hasn't been used in a transaction yet. Node $A$ has generated it so that it is ready to be used in the next transaction.
	\item[] $\mathbf{KP_{An-1}}$ is node $A$'s key packet up to transaction $n-1$, and includes keys for as many transactions as node $A$ feels is appropriate in order to receive verification.
	\item[] $\mathbf{loc}$ is node $A$'s current claimed GPS coordinates for which it is seeking verification.
	\item[] $\mathbf{NP_{An-1}}$ is node $A$'s \textit{Nonce Packet}, a subset of its \textit{Nonce List} (section \ref{sssec:nonce_list}). A Nonce Packet is the list of the nonces used to generate node $A$'s most recent IDs, up to $n-1$, that node $A$ is willing to share with the Verifier. 
\end{itemize}

\null
The goal of the verification stage is for the Verifier to either accept or reject the location that the user is claiming. Given $ID_{A}[n-1]$ and $KP_{An-1}$, a Verifier is able to retrieve node $A$'s previous transactions, and the transactions of all of its alibis. This will allow the Verifier to recursively inspect the transactions of all alibis used in a node's transactions, until it is satisfied that the location can be verified or rejected. This recursive inspection can be visualised as a tree, as shown in figure \ref{fig:tree}.

>>>>

This chapter details the design of a decentralised location proof system. It starts with a general overview of the proposed system, before explaining in detail the three major components: Identities (section \ref{sec:identities}), Transactions (section \ref{sec:transactions}), and Verification (section \ref{ssec:verification}).

@@

\section{Identities} \label{sec:identities}
In order to preserve users' privacy, a user will only ever use an identity for one transaction, before generating a new one. This prevents curious users from watching the public blockchain for a known identity and tracking it. However, to prevent identity theft, it is important for a Verifier to be able to prove that a mobile node is the owner of each identity. This is achieved using a public/private key pair for each mobile node.

@@

\subsection{Identity duplication}
Since all identities are generated from random nonces, there is nothing to prevent two nodes from generating the same identity and using it in different transactions. It is therefore possible that during verification, a Verifier node may find multiple transactions with the same ID while searching the blockchain. Verifiers are provided with decryption keys from the requesting node for the transactions they are searching for, which will only successfully decrypt one of the transactions with the duplicate ID. A Verifier will try to decrypt each one until it finds the one that can be decrypted successfully.

\section{Transactions} \label{sec:transactions}
During an exchange between two nodes, a number of different items must be shared and calculated. Figure \ref{fig:transaction} describes and explains an honest, successful exchange, assuming an ad-hoc network has already been set up between nodes $A$ and $B$.

@@

To abort the exchange, node $A$ terminates the ad-hoc network with node $M$, and will not publish anything onto the blockchain. This means that even if node $M$ fabricates some data from node $A$ and publishes a transaction onto the blockchain, the matching transaction from node $A$ will not be present, so node $M$'s transaction will be disregarded by any Verifiers.

\begin{figure}[H]
\resizebox {\columnwidth} {!} {\input{diagrams/aborted_transaction.tex}}
\caption{An aborted transaction due to malicious node $M$}
\label{fig:aborted_transaction}
\end{figure}

@@

\begin{figure}[H]
\begin{center}
\resizebox {0.75\columnwidth} {!} {\input{diagrams/verify_request.tex}}
\caption{Verification request}
\label{fig:verify_request}
\end{center}
\end{figure}

\begin{itemize}[noitemsep,topsep=0pt]
	\item[] $\mathbf{ID_{A}[n-1]}$ is the ID of node $A$'s most recently published transaction. Note that $ID_A[n]$ has already been generated, but has not been used in a transaction yet. Node $A$ has generated it so that it is ready to be used in the next transaction.
	\item[] $\mathbf{KP_{An-1}}$ is node $A$'s key packet up to transaction $n-1$, and includes keys for as many transactions as node $A$ feels is appropriate in order to receive verification.
	\item[] $\mathbf{loc}$ is node $A$'s current claimed GPS coordinates for which it is seeking verification.
	\item[] $\mathbf{NP_{An-1}}$ is node $A$'s \textit{Nonce Packet}, a subset of its \textit{Nonce List} (section \ref{sssec:nonce_list}). A Nonce Packet is the list of the nonces used to generate node $A$'s most recent IDs, up to $n-1$, that node $A$ is willing to share with the Verifier. 
\end{itemize}

\null
The goal of the verification stage is for the Verifier to either accept or reject the location that the user is claiming. Given $ID_{A}[n-1]$ and $KP_{An-1}$, a Verifier is able to retrieve node $A$'s previous transactions, and the transactions of all its alibis. This will allow the Verifier to recursively inspect the transactions of all alibis used in a node's transactions, until it is satisfied that the location can be verified or rejected. This recursive inspection can be visualised as a tree, as shown in figure \ref{fig:tree}.
